EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-10 paper/paper.tex

In this paper, we introduce EasyMerge, a new tool to refactor code clones. EasyMerge is built on top of AST-based clone detection algorithm
\end{abstract}

@@

\section{Clone Code Detection}

@@

\section{Conclusions}

\section{Future Work}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

>>>>

In this paper, we introduce EasyMerge, a new tool to refactor code clones. EasyMerge is built on top of AST-based anti-unification clone detection algorithm and 
refactors software projects written in Python. It adds intelligence to code clone refactoring by categorizing clones and generating refactoring recommendations
based on evaluation of external variable references and function calls. It copes with features of Python language and can deal with clone segments in functions,
classes, and across different scopes. It ensures functionality-wise consistency before and after refactoring and provide warnings when potential refactoring could lead to
unwanted complexity or cause readability issues.
\end{abstract}

@@

\section{CloneDigger}

@@

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
